\documentclass{resume}

\usepackage[T1]{fontenc}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{microtype}

\name{Raghav Subramaniam}
\contact{1234 Main St, Somewhere, CA 90000 ~$\cdot$~ 123 456 7890 ~$\cdot$~ someone@provider.com}

\begin{document}

\begin{rSection}{Education}

    \begin{rEducation}{Stanford University}{Stanford, CA}{Jun 2018}
        M.S. in Electrical Engineering. GPA 0.00/4.30.
    \end{rEducation}

    \begin{rEducation}{Cornell University}{Ithaca, NY}{May 2015}
        B.S. in Electrical \& Computer Engineering. GPA 0.00/4.30.
    \end{rEducation}

\end{rSection}

\begin{rSection}{Experience}

    \begin{rExperience}{Lead Computer Vision Engineer}{Mar 2017--Present}{SafelyYou, Inc.}{Berkeley, CA}
        \item Developed deep learning algorithms for video-based fall detection for dementia patients.
        \item Worked closely with the founders and COO in order to launch a working fall detection product.
        \item Trained, fine-tuned, and iterated on convolutional neural network-based detection algorithms using Python and Caffe.
        \item Deployed convolutional neural networks on-prem for real-time detection.
        \item Took ownership of other engineering processes such as building and shipping computer hardware, interfacing with camera APIs, and maintaining a central documentation repository.
    \end{rExperience}
    
    \begin{rExperience}{Research Assistant}{Jun 2016--Mar 2017}{Gevaert Lab, Stanford University}{Stanford, CA}
        \item Developed deep learning algorithms for brain tumor segmentation.
        \item Built an extensible pipeline for medical image processing and computer vision using Python and TensorFlow.
        \item Gave two conference talks based on my work.
    \end{rExperience}

    \begin{rExperience}{Teaching Assistant}{Jan 2015--May 2015}{Department of Computer Science, Cornell University}{Ithaca, NY}
        \item Helped teach undergraduate/graduate-level computer vision course.
        \item Developed homework and test questions, held office hours, and graded papers.
    \end{rExperience}

    \begin{rExperience}{Research Assistant}{Sep 2013--May 2015}{Goldberg Lab, Cornell University}{Ithaca, NY}
        \item Worked with an interdisciplinary group of ten, including biologists and engineers, on experiments about the behavioral and neurological basis of motor learning in animals.
        \item Contributed to design and assembly of custom joysticks for use in novel experiments on forelimb motor learning in mice.
        \item Programmed a large-scale, real-time system in LabVIEW for training mice to use joysticks.
    \end{rExperience}

    % \begin{rExperience}{Student Intern---Electrical Engineering}{Jun 2013--Aug 2013}{Sandia National Labs}{Albuquerque, NM}
    % \item Collaborated with two other electrical engineers on weapons subsystem testing.
    % \end{rExperience}

\end{rSection}

\begin{rSection}{Awards and Presentations}

    {\em 3-D Convolutional Neural Networks for Glioblastoma Segmentation}, Workshop on Multimodal Learning for Clinical Decision Support, MICCAI 2016, {\em Athens, Greece}, {\bf Oct 2016}.

    Best Mobile Hack, BrickHack, Rochester Institute of Technology, {\em Rochester, NY}, {\bf May 2016}.

\end{rSection}

\begin{rSection}{Skills}

    Python, Caffe, TensorFlow, Linux, Bash, Git, Vim

\end{rSection}

\end{document}
